% $Id: cv_work_en.tex 2008/10/08 izimine Exp$ 

\documentclass[a4paper,11pt,oneside]{article}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{array}
\usepackage{times}

% change default font to Helvetica
\renewcommand{\rmdefault}{\sfdefault}

%% change the default second level itemize mark
%\makeatletter
\renewcommand{\labelitemii}{$\circ$}
%\makeatother

\usepackage[left=1in,top=1in,right=1in,bottom=1in]{geometry}

\begin{document}

\pagestyle{empty}

\begin{center}
{\large \textbf{Curriculum Vitae}}\\

\vspace{2mm}

August 2009

\end{center}

%\vspace{10mm}

\subsection*{Personal Data}
%\begin{tabular}{>{\itshape}l l}
\begin{tabular}{>{\itshape}p{3cm} p{12cm}}
Name:        & Zimine Ivan \\
Birth Date:  & 30 July 1975 \\
%Birth Place: & Russia \\
Nationality: & Switzerland \\
Address:     & Philips Electronics Japan, Ltd., Healthcare\\
             & 2-13-37 Konan, Minato-ku, Tokyo, Japan 108-8507\\
%Tel:         & (81)3 3740 3213 \\
Email:       & ivan.zimine@philips.com \\
%Languages:   & French, English, Russian \\
\end{tabular}

\vspace{5mm}

\subsection*{Education}
\begin{tabular}{>{\itshape}p{3cm} p{12cm}}

1998--2003 & Dpt.~of~Radiology, Geneva University Hospitals
             (Dr.~F.~Lazeyras, Dr.~M.~Seeck); 
             Group of Applied Physics, University of Geneva
             (Prof.~P.~Descouts).
             PhD Thesis: "\textit{Epileptic Focus Localization
             Using EEG-triggered Functional MRI}"\\

1997--1998 & Dpt.\ of Radiology, Geneva University Hospitals; 
              Group of Applied Physics, University of Geneva.
              Dipl\^{o}me \`{e}s sciences physiques: 
              "\textit{\mbox{Motion} correction in Functional 
              Magnetic Resonance Imaging}" 
              (MSc)\\

1993--1997 & Dpt. of Condensed Matter Physics, University of Geneva. 
              License \`{e}s sciences physiques: "\textit{Etude des effets
              de dopage par fluor sur Bi(2212), poudre et monocristaux}"
              (BSc)\\

\end{tabular}

\vspace{5mm}

\subsection*{Employment}
%\begin{tabular}{>{\itshape}l p{12cm}}
\begin{tabular}{>{\itshape}p{3cm} p{12cm}}

05/2007--current & MR clinical scientist, Philips Healthcare. 
        (Advanced~neuro~applications)\\ 

10/2004--04/2007 & Postdoctoral fellow, Dpt.\ of Neuroradiology,
           National Neuroscience Institute, Singapore. % (ref.\ Dr.~X.~Golay):
           (quantitative fMRI, arterial spin labeling, 
           regional \mbox{perfusion} imaging)\\

08/2003--08/2004 & Postdoctoral fellow, Dpt.\ of~Radiology,
            Geneva University \mbox{Hospitals}. % (ref.\ Dr.~F.~Lazeyras):
            (image analysis, brain anatomy)\\

%2001--2003: &  Research fellow, Dpt. of Radiology, Geneva
%University Hospitals: system administration (solaris, linux), MR research data
%management, user support (Anatomist/BrainVISA, MEDx, IDL).\\

08/1998--06/2003  & Research fellow, Dpt.~of~Radiology, Geneva
University Hospitals. (MR~sequence development, image analysis)\\
%Marconi), post-processing software development (IDL), user support (MEDx, SPM, IDL) \\
\end{tabular}

\vspace{5mm}

\subsection*{Professional membership}
\begin{itemize}
\item International Society for Magnetic Resonance in Medicine 
\item IEEE Engineering in Medicine and Biology
\end{itemize}

\pagebreak


\subsection*{Publications}

\subsubsection*{Journal articles}

\begin{enumerate}

\item S.~M.~Chng, E.~T.~Petersen, I.~Zimine, Y.~Y.~Sitoh, C.~C.~Lim, X.~Golay.
\textit{Territorial arterial spin labeling in the assessment of collateral
circulation: comparison with digital subtraction angiography.} Stroke
\textbf{39}:3248--54 (2008).

\item J.~Abutalebi, J.M.~Annoni, I.~Zimine, A.J.~Pegna, M.L.~Seghier, 
H.~Lee-Jahnke, F.~Lazeyras, S.F.~Cappa, A.~Khateb. 
\textit{Language control and lexical competition in bilinguals: 
an event-related FMRI study.} Cereb Cortex \textbf{18}:1496--50 (2008).

\item I.~Zimine, E.~T.~Petersen, X.~Golay.
\textit{Dual vessel arterial spin labeling scheme for regional perfusion
imaging.} Magn Reson Med \textbf{56}: 1140--1144 (2006).

\item E.~T.~Petersen, I.~Zimine, Y.-C.~L.~Ho, X.~Golay.
\textit{Non-invasive measurement of perfusion: a critical review of
arterial spin labeling techniques.}
Br J Radiol.\ \textbf{79}: 688--701 (2006).

\item H.~Juch, I.~Zimine, M.~L.~Seghier, F.~Lazeyras, J.~H.~Fasel.
\textit{Anatomical variability of the lateral frontal lobe surface:
implication for intersubject variability in language neuroimaging.}
Neuroimage \textbf{24}: 504--514 (2005).

\item  M.~L.~Seghier, F.~Lazeyras, A.~J.~Pegna, J.~M.~Annoni,
I.~Zimine, E.~Mayer, C.~M.~Michel, A.~Khateb.
\textit{Variability of fMRI activation during a phonological and
semantic language task in healthy subjects.} Hum Brain Mapp.\ 
\textbf{23}: 140--155 (2004)

\item M.~K.~Ivancevic, I.~Zimine, X.~Montet, J.~N.~Hyacinthe,
F.~Lazeyras, D.~Foxall and J.-P.~Vall\'{e}e.
\textit{Inflow effect correction in fast gradient-echo perfusion
imaging.} Magn Reson Med.\ \textbf{50}: 885--891 (2003).

\item M.~K.~Ivancevic, I.~Zimine, D.~Foxall, G.~Lecoq,
A.~Righetti, D.~Didier, and J.-P.~Vall\'{e}e.
\textit{Inflow effect in first-pass cardiac and renal MRI.}
J Magn Reson Imaging \textbf{18}: 372--376 (2003).

\item I. Zimine, M. L. Seghier, M. Seeck and F.~Lazeyras.
\textit{Brain Activation using triggered event-related fMRI.}
Neuroimage \textbf{18}:410--415 (2003).

\item M.~K.~Ivancevic, I.~Zimine, F.~Lazeyras, D.~Foxall and
J.-P.~Vall\'{e}e.
\textit{FAST sequences optimization for contrast media pharmacokinetic
quantification in tissue.} J Magn Reson Imaging
\textbf{14}:771-778 (2001).

\item N.~Valenza, R.~Ptak, I.~Zimine, M.~Badan, F.~Lazeyras and
A.~Schnider.
\textit{Dissociated active and passive tactile shape recognition:
a case study of pure tactile apraxia.} Brain \textbf{124}:2287--2298
(2001)

\item F.~Lazeyras, I.~Zimine, O.~Blanke, S.~Perrig and M.~Seeck,
\textit{Functional MRI with simultaneous EEG recording: Feasibility and
application to motor and visual activation.} J Magn Reson Imaging
\textbf{13}:943--948 (2001).

\item F.~Lazeyras, O.~Blanke, S.~Perrig, I.~Zimine, X.~Golay, J.~Delavelle,
C.M.~Michel, N.~de~Tribolet, J.G.~Villemure and M.~Seeck,
\textit{EEG-triggered functional MRI in patients with pharmacoresistant
epilepsy.} J Magn Reson Imaging \textbf{12}:177--185 (2000).

\item F.~Lazeyras, O.~Blanke, I.~Zimine, J.~Delavelle, S.~Perrig and M.~Seeck,
\textit{MRI, $^1$H-MRS and functional MRI in a patient during
and after prolonged nonconvulsive seizure activity.} Neurology
\textbf{55}:1677--1682 (2000).

\end{enumerate}

% maybe add papers with explicit aknowledgements
% Golay, Yoshiura, Ho, ...

\subsubsection*{Peer-reviewed conference abstracts (as 1st author)} 
\begin{enumerate}

\item I.~Zimine, T.~Yoshiura, A.~Hiwatashi, T.~Noguchi, M.~Van~Cauteren.
\textit{Utility of shared rotating control acquisition for territorial
ASL}, 17th ISMRM, Hawaii, 2009, p.~3653

\item I.~Zimine, E.~T.~Petersen, and X.~Golay.
\textit{Subtraction errors in regional perfusion imaging using a single
control acquisition}, Joint Meeting ISMRM-ESMRMB, Berlin, 2007, p.~3490

\item I.~Zimine, E.~T.~Petersen, and X.~Golay.
\textit{Dual Vessel Arterial Spin Labeling Scheme for Regional Perfusion
Imaging}, 8th International Conference on XeCT and Related CBF Techniques,
Cambridge, 2006

\item I.~Zimine, E.~T.~Petersen, and X.~Golay.
\textit{Dual Vessel Arterial Spin Labeling Scheme for Regional Perfusion
Imaging}, 14th ISMRM, Seattle, 2006, p.~669.

\item I.~Zimine, E.~T.~Petersen, F.~Sardou, and X.~Golay.
\textit{Automatic Planning for Regional Perfusion Imaging}, 
14th ISMRM, Seattle, 2006, p.~3426.

\item I.~Zimine, E.~T.~Petersen, Y.~C.~L.~Ho and X.~Golay.
\textit{Partial volume effects in VASO-fMRI}, 13th ISMRM, Miami,
2005, p.~493.

\item I.~Zimine, H.~Juch, J.~H.~Fasel, K.~O.~Lovblad and F.~Lazeyras.
\textit{Study of sulcal and anatomical landmarks variability in the
inferior frontal lobe}, 12th ISMRM, Kyoto, 2004, p.~1322.

\item I.~Zimine, F.~Lazeyras, M.~L.~Seghier, G.~Lantz and M.~Seeck.
\textit{Combined triggered EEG-fMRI and $^1$H spectroscopy in the
localization of extratemporal epileptic activity}, 11th ISMRM,
Toronto, 2003, p.~2027.

\item I.~Zimine, M. L. Seghier, M.~Seeck, F.~Lazeyras.
\textit{Feasibility of triggered event-related fMRI.}, 19th ESMRMB,
Cannes, 2002, Nr. 350.

\item I.~Zimine, F.~Lazeyras, S.~Perrig and P.~Descouts,
\textit{FMRI feasibility with simultaneous EEG recording}, 
8th ISMRM, Denver, 2000, p.~819.

\item I.~Zimine, F.~Lazeyras, J.-P.~Vall\'{e}e, D.A.~R\"{u}fenacht
and P.~Descouts \textit{Effect of Motion Correction on the FMRI Activated
Areas}, 7th ISMRM, Philadelphia, 1999, p.~1678.

\end{enumerate}

\subsubsection*{Invited Talks/Presentations}
\begin{itemize}

\item I.~Zimine. \textit{Towards quantitative perfusion imaging using
QUASAR}, Lunch symposium, Japanese Society of Magnetic Resonance in
Medicine, Kobe, Japan, September 28, 2007

\item I.~Zimine. \textit{MRI in Dementia -- Quantitative and Novel
Methodologies}, 5th Asia-Pacific Regional Meeting of the International
Working Group on the Harmonization of Dementia Drug Guidelines, Makati
City, Philippines, October 19-20, 2006.

%\item I.~Zimine et al. \textit{Automatic planning for Regional Perfusion
%Imaging}, 1st Singaporean-French Biomedical Imaging Workshop, Biopolis,
%Singapore October 12-13, 2006.

\item I.~Zimine. \textit{Advances in Quantitative fMRI}, 
SingHealth, NHG and NUS, Combined Scientific Meeting 2005, Singapore.

\end{itemize}

%\pagebreak

%\subsection*{Awards and Fellowships}
%\begin{itemize}
%\item 2006 - Advanced Researcher fellowship, Swiss Foundation for Grants in 
%    Biology and Medicine (Swiss National Science Foundation partner)
%\item 2006 - ISMRM Student stipend 
%\item 2005 - ISMRM Student stipend
%\item 2004 - ISMRM Student stipend
%\end{itemize}


%\subsection*{Courses and Workshops}
%\begin{itemize}
%\item GyroTools Pulse Programming Course, June 20-24, 2005
%\item Responsible care and use of laboratory animals, March 24 - April 8, 2005
%\item CITI course in The Protection of Human Research Subjects, November, 2004
%\item Workshop on Functional Brain Imagery of Cognitive Processes, January
%27-31, 2003
%\item Summer School on Mathematical Morphology, September 9-13, 2002
%\item IDL 5.1 Advanced programming course, October 14-15, 1998
%\end{itemize}

\end{document}
